### 2016-07-27 syntax.tex
cheers

\heading{Set-multiplicity Data Structures. }
Our particular focus will be on data structures that support multiplicity queries, of which set-membership queries are a special case.  
\begin{definition} A \emph{set-multipicity data structure} is a data structure with $D=\mathbb{N}$ and where $\calQ=\{q_x \,|\, x \in \univ\}$ where $q_x(S)$ is defined to be the multiplicity of~$x$ in the multiset~$S$.
\hfill\dqed
\end{definition}
%
%\todo{Readdress issue of representation size.  A general statement might be something like `` The \emph{size} of a set-representation is the maximum (bit)length of any~$M$ that can be output by $\Rep$.''  But all of the natural constructions will have representation whose size will not depend on the coins of $\Rep$, i.e. they depend on $|S|$, number of hash functions, desired error rate. }

>>>>

\def\bin{{\sf Bin}}
\heading{Trivial attacks, and error-probability vs.\ error-rate. } 
Let~$\Pi$ be a scheme that is $(1-\epsilon)$-correct, and consider an attack that 
asks random queries $q_1,q_2,\ldots,q_T$, i.e., uniform samples from~$\calQ$.
%The expected number of random queries needed to
%find a error is $1/\epsilon$ tries; thus, an attacker making $O(t/\epsilon)$ queries succeeds with constant probability (almost always).
%Actually, it seems worthwhile to formalize this. 
Let $\mathrm{Err}_i$ be a random variable indicating the event $\Qry(M,\aux,q_i)\neq q_i(S)$.  
The $(1-\epsilon)$-correctness of~$\Pi$ guarantees that the probability that $\mathrm{Err}_i=1$ is at most~$\epsilon$, 
and it is tempting to model the~$\mathrm{Err}_i$ as i.i.d. Bernoulli trials with success probability~$\epsilon$.
However, a moment's reflection shows that this is not the case.  Concretely, consider the following scheme.  Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$.  For the queries, let $\calQ = \{q_x\colon \calS \to \bits \,|\, \forall x \in \univ\}$ where $\forall S \in \calS$ the predicate $q_x(S)=1 \Leftrightarrow x \in S$.  Let $\Rep(S)$ pick a random element~$s \in S$, and return $M = S \setminus \{s\}$ and $\aux = \emptystring$.  To respond to queries, let~$\Qry(M,\aux,q_x)=1$ iff $x \in M$.  It is easy to see that this scheme is $1/n$-correct; for any fixed~$S$, there are exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the coins of~$\Rep$) of causing a correctness error, and the remaining $|\univ|-n$ queries have probability zero of causing an error.  Moreover, once the coins of~$\Rep$ are fixed, there is exactly \emph{one} query that will cause an error.  Thus for random queries from~$Q$, for all~$i\in[T]$ we have $\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.

This example is contrived, but it highlights the important difference
between error-probability and error-rate.  In particular, the
error-probability~$\epsilon$ is measured only over the coins
of~$\Rep$, for a fixed~$S$ and query~$q$.
Once the coins of~$\Rep$ are fixed, it is not straightforward how to
connect~$\epsilon$ to events that depend on other sources of
randomness. \tsnote{Not sure if there's more to say in this section, or if what's here is already too much.}
\heading{Set-multiplicity Data Structures. }
Our particular focus will be on data structures that support multiplicity queries, of which set-membership queries are a special case.  
\begin{definition} A \emph{set-multipicity data structure} is a data structure with $D=\mathbb{N}$ and where $\calQ=\{q_x \,|\, x \in \univ\}$ where $q_x(S)$ is defined to be the multiplicity of~$x$ in the multiset~$S$.
\hfill\dqed
\end{definition}
%
%\todo{Readdress issue of representation size.  A general statement might be something like `` The \emph{size} of a set-representation is the maximum (bit)length of any~$M$ that can be output by $\Rep$.''  But all of the natural constructions will have representation whose size will not depend on the coins of $\Rep$, i.e. they depend on $|S|$, number of hash functions, desired error rate. }
